Understanding the impacts of video-guided activities on parent-child interaction

### 2019-09-16 paper/manuscript.tex
Bayesian regression reporting done

The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software (Team, 2014).
The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera.
Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA.
Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA.
If more than 3 seconds elapsed between bids, they were coded as separate attempts.
An episode of joint attention was considered \emph{passive} if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent.
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention.
A joint attention episode was considered \emph{coordinated} if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
Full details of our guidelines for coding joint attention are available in \href{https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing}{SI}.

@@

We fit a mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using lme4 (Bates, Mächler, Bolker, \& Walker, 2015).
There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, \(\beta=\)-0.11, t(52.4) = 4.22, \emph{p}\textless{}.001).
There were no significant effects of age, gender, or parent's level of education.
A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 0.32, \(\beta=\)-8.73, t(55) = 2.67, \emph{p}=.001), with no other significant effects.
Figure \ref{fig:e1lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta= 56.01\), t(40.4)=2.30, \emph{p}\textless{}.05), with parents using more words in the Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,253{]}) than in the Control condition (mean: 165, bootstrapped 95\% CI: {[}139,192{]}).
The means of the lexical diversity measures are reported in Table \ref{tab:e1tab}.

\caption{\label{tab:e1tab}Lexical diversity measures in Experiment 1.}
\centering
\begin{tabular}{l|r|r|r|r|r|r|r|r}
\hline
Condition & TTR (M) & (sd) & MTLD (M) & (sd) & Types (M) & (sd) & Tokens (M) & (sd)\\
\hline
No Video & 0.43 & 0.10 & 27.09 & 15.33 & 67.33 & 22.94 & 165.10 & 75.15\\
\hline
Activity Video & 0.32 & 0.09 & 17.87 & 6.28 & 67.37 & 19.01 & 225.43 & 76.07\\
\hline
\end{tabular}
\end{table}

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
This lme4 model included random intercepts per video.
There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, \(\beta=3.51\), t(40.30) = 2.95, \emph{p}\textless{}.01).
There were no other significant effects.

Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.83\), t(41.50) = 2.22, \emph{p}\textless{}.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

@@

We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 (Bates et al., 2015).
There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.48, \(\beta=-0.09\), t(8.60) = 3.33, \emph{p}=0.01).
There was no significant effect of age, nor a significant interaction.
The preregistered regression predicting the number of tokens used by parents revealed no significant effects.
An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: 12.98, bootstrapped 95\% CI: 11.77, 14.18; \(\beta=3.11\), t(80) = 3.52, \emph{p}=0.00)) than after the Science Video (mean: 9.88, 95\% CI: {[}8.69, 11.11{]}, \(\beta=3.11\), t(80) = 3.52, \emph{p}\textless{}.001).
There were no other significant effects on parental bids for JA.

In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.49\), t(80) = 2.70, \emph{p}=0.01), with more episodes of JA occurring after the Activity Video (mean: 8.78, 95\% CI: {[}7.89, 9.67{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.57, 8.06{]}).
There was also a significant main effect of age (\(\beta=-5.27\), t(80) = 3.48, \emph{p}=0.00), showing that the number of episodes of JA decreased with the child's age.
However, a significant interaction of age and condition (\(\beta=5.92\), t(80) = 2.61, \emph{p}=0.01), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the number of episodes of coordinated JA found a significant main effect of condition (\(\beta=1.37\), t(80) = 2.59, \emph{p}=0.01), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.71, 95\% CI: {[}5.92, 7.61{]}) than after the Control Video (mean: 5.34, 95\% CI: {[}4.72, 5.98{]}).
There was no significant effect of age, but there was a significant interaction of age and condition (\(\beta=5.24\), t(80) = 2.40, \emph{p}=0.02), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
The regression predicting the total duration of coordinated JA episodes revealed no significant effects.

In the regression predicting the number of episodes of passive JA, there was a main effect of age (\(\beta=0.11\), t(6.90) = 0.27, \emph{p}=0.80), showing that older children had more episodes of passive JA with their caregiver.
The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=0.40\), t(80) = 0.16, \emph{p}=0.88), revealing that older children spent more time in passive JA with their caregiver.
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.

@@

\caption{\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2. Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition.}\label{fig:e2ja-coord}
\end{figure}

@@

>>>>

The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software (Team, 2014).
The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera.
Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA.
Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA.
If more than 3 seconds elapsed between bids, they were coded as separate attempts.
An episode of joint attention was considered \emph{passive} if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent.
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention.
A joint attention episode was considered \emph{coordinated} if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
Full details of our guidelines for coding joint attention are available in SI.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
There were no significant effects of age, gender, or parent's level of education.
A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 27.09, \(\beta=\)-8.62, 95\% CI={[}-15.15,-2.01{]}), with no other significant effects.
Figure \ref{fig:e1lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 56.36, 95\% CI={[}14.02,96.32{]})), with parents using more words in the Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,252{]}) than in the Control condition (mean: 165, bootstrapped 95\% CI: {[}139,193{]}).

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
This lme4 model included random intercepts per video.
There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, \(\beta=3.44\), 95\% CI={[}1.12,5.80{]}).

Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.84\), 95\% CI={[}0.23,3.44{]}), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

@@

We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 (Bates, Mächler, Bolker, \& Walker, 2015).
There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15,-0.03{]}).
There was no significant effect of age, nor a significant interaction.
The preregistered regression predicting the number of tokens used by parents revealed no significant effects.
An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% CI: 11.74, 14.21; \(\beta=3.06\), 95\% CI = {[}0.96,5.06{]}) than after the Science Video (mean: 9.88, 95\% CI: {[}8.71, 11.07{]}).
There were no other significant effects on parental bids for JA.

In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.49\), 95\% CI = {[}0.26,2.78{]}), with more episodes of JA occurring after the Activity Video (mean: 8.79, 95\% CI: {[}7.95, 9.67{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.54, 8.05{]}).
There was also a significant main effect of age (\(\beta=-5.02\), 95\% CI = {[}-8.23,-1.41{]}), showing that the number of episodes of JA decreased with the child's age.
However, a significant interaction of age and condition (\(\beta=5.67\), 95\% CI = {[}0.50,10.71{]}), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the number of episodes of coordinated JA found a significant main effect of condition (\(\beta=1.36\), 95\% CI = {[}0.16,2.58{]}), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.71, 95\% CI: {[}5.90, 7.56{]}) than after the Control Video (mean: 5.34, 95\% CI: {[}4.68, 6.02{]}).
There was no significant effect of age, but there was a significant interaction of age and condition (\(\beta=5.34\), 95\% CI = {[}0.80,10.22{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
The regression predicting the total duration of coordinated JA episodes revealed no significant effects.

In the regression predicting the number of episodes of passive JA, there was a main effect of age (\(\beta=-2.72\), 95\% CI = {[}-5.07,0.19{]}), showing that older children had more episodes of passive JA with their caregiver.
The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=-17.70\), 95\% CI = {[}-32.73,-1.79{]}), revealing that older children spent more time in passive JA with their caregiver.
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.

@@

\caption{The number of episodes of coordinated JA by condition and age in Experiment 2. Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition.}\label{fig:e2ja-coord}
\end{figure}

@@

\leavevmode\hypertarget{ref-rstanarm}{}%
Goodrich, B., Gabry, J., Ali, I., \& Brilleman, S. (2018). Rstanarm: Bayesian applied regression modeling via Stan. Retrieved from \url{http://mc-stan.org/}
